Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-30 paper.qmd
Revise Figure 8 (b), still not useful..need to update

@@

## To obtain the standardise counts within hexbins
counts_df1 <- hb_obj_scurve1$std_cts
df_bin_centroids1 <- extract_hexbin_centroids(
  centroids_df = all_centroids_df1, 
  counts_df = counts_df1) |>
  filter(drop_empty == FALSE)

@@

@@

## To obtain the standardise counts within hexbins
counts_df2 <- hb_obj_scurve2$std_cts
df_bin_centroids2 <- extract_hexbin_centroids(
  centroids_df = all_centroids_df2, 
  counts_df = counts_df2) |>
  filter(drop_empty == FALSE)

@@

@@

## To obtain the standardise counts within hexbins
counts_df3 <- hb_obj_scurve3$std_cts
df_bin_centroids3 <- extract_hexbin_centroids(
  centroids_df = all_centroids_df3, 
  counts_df = counts_df3) |>
  filter(drop_empty == FALSE)

@@

```{r}
#| label: bin-counts-scurve
cell_count_scurve <- ggplot(df_bin_centroids_scurve, 
                            aes(x = reorder(as.factor(hexID), 
                                            -std_counts), 
                                y = std_counts,
                                group = "1")) + 
  geom_line() + 
  geom_hline(yintercept = benchmark1, color = "black", linewidth=0.5, alpha = 0.5) +
  xlab("hexagon id (re-ordered)") + 
  ylab("standardized bin count") +
  ggtitle("(b)") +
  theme(aspect.ratio = 0.75,
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12, angle = 90),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 12))
```

>>>>

a1_1 <- calc_bins_y(
  bin1 = 7, 
  r2 = r2,
  q = 0.12
)$a1

@@

## To obtain the standardise counts within hexbins
counts_df1 <- hb_obj_scurve1$std_cts
df_bin_centroids1 <- extract_hexbin_centroids(
  centroids_df = all_centroids_df1, 
  counts_df = counts_df1) |>
  filter(drop_empty == FALSE) |>
  mutate(a1 = a1_1)

@@

a1_2 <- calc_bins_y(
  bin1 = 11, 
  r2 = r2,
  q = 0.07
)$a1

@@

## To obtain the standardise counts within hexbins
counts_df2 <- hb_obj_scurve2$std_cts
df_bin_centroids2 <- extract_hexbin_centroids(
  centroids_df = all_centroids_df2, 
  counts_df = counts_df2) |>
  filter(drop_empty == FALSE) |>
  mutate(a1 = a1_2)

@@

a1_3 <- calc_bins_y(
  bin1 = 17, 
  r2 = r2,
  q = 0.05
)$a1

@@

## To obtain the standardise counts within hexbins
counts_df3 <- hb_obj_scurve3$std_cts
df_bin_centroids3 <- extract_hexbin_centroids(
  centroids_df = all_centroids_df3, 
  counts_df = counts_df3) |>
  filter(drop_empty == FALSE) |>
  mutate(a1 = a1_3)

@@

```{r}
#| label: bin-counts-scurve

df_bin_centroids_all <- bind_rows(
  df_bin_centroids1,
  df_bin_centroids2,
  df_bin_centroids3
)

cell_count_scurve <- ggplot(df_bin_centroids_all, 
                            aes(x = reorder(as.factor(hexID), 
                                            -std_counts), 
                                y = std_counts,
                                group = a1,
                                color = a1)) + 
  geom_line() + 
  geom_hline(yintercept = benchmark1, color = "black", linewidth=0.5, alpha = 0.5) +
  scale_colour_continuous_sequential(palette = "Magenta") +
  xlab("hexagon id (re-ordered)") + 
  ylab("standardized bin count") +
  ggtitle("(b)") +
  theme(aspect.ratio = 0.75,
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12, angle = 90),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(size = 12))
```
